Group Fou\\*R* Term Project

### 2018-12-16 Draft.Rmd
.

Through the shiny app, it is understood that
* 70% of import value from China is coming from 8 products 
* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
* %70 is from commodities and mineral fuels for import from Russia
* Only commodities constitute 43% of total import of Russia
* Vehicles other than railway is the top product imported from Germany
* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles

>>>>

Through the shiny app, it is understood that

* 70% of import value from China is coming from 8 products 
* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
* %70 is from commodities and mineral fuels for import from Russia
* Only commodities constitute 43% of total import of Russia
* Vehicles other than railway is the top product imported from Germany
* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles
